Inferring Fine Scale Behaviors Within Hierarchical Hidden Markov Models

### 2020-05-18 Report/Sections/simulation.tex
Update simulation study

\begin{figure}[h!]
	\centering
	\includegraphics[height=7.5in]{../Plots/smoothed_v.png}
	\caption{From top to bottom: dive depth, unsmoothed vertical velocity, smoothed vertical velocity, ODBA, and the sum of low-frequency Fourier coefficeints of the ODBA for a randomly selected dive of a killer whale.}
	\label{fig:smoothing}
\end{figure}

>>>>

To test this method, dive and acceleration data was simulated using the following procedure:

\begin{enumerate}
	\item 100 dive durations were simulated using a gamma distribution using an HMM generative model and the following parameters:

	\begin{align*}
		\Gamma &= \begin{pmatrix} 0.4 & 0.6 \\ 0.6 & 0.4 \end{pmatrix} \\
		% 
		&Y_t|X_t \sim \text{Gamma} \\
		\bbE(Y_t|X_t = 1) &= 15, \quad \bbE(Y_t|X_t = 2) = 60 \\
		%
		\bbV(Y_t|X_t = 1) &= 25, \quad \bbV(Y_t|X_t = 2) = 100
	\end{align*}
\end{enumerate}
